---
title: "ADImaging"
author: "Qin"
date: "2019/10/23"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.Introduction 
  ADImaging dataset is downloaded on the http://adni.loni.usc.edu/. There are 254 samples and 157 variables: 5 demographic information(age, gender, years of education , marital status and APOE4), cortical thickness in 150 brain regions, total incranial volume(TIV) and disease stage(DX).**The key variable is "ID".**
  
## 2.Data
```{r echo = FALSE, warning = FALSE}
#Import the data
library(readxl)
library(knitr)
library(tidyverse)
library(nycflights13)
library(ggplot2)
ADNI <- read_excel("ADImaging.xlsx")
```

###Overview
```{r echo = FALSE, warning = FALSE}
View(ADNI)
kable(ADNI[1:5,2:8],caption="independent variables")
```

### Data Check anf Cleaning
```{r echo = FALSE, warning = FALSE}
colnames(ADNI)
ADNI[1:6, ]
```

```{r echo = FALSE, warning = FALSE}
#Only focus on demographic information of AD patients, and order by IDs
#"DX":1-HC/2-EMCI/3-LMCI/AD
ADNI_demographic <-ADNI %>%
   select(ID, DX, AGE, GENDER, EDUCAT, MARRY) %>%
   arrange(ID, DX)
```

Question1:What is the gender of the AD patient?
```{r echo = FALSE, warning = FALSE}
#"GENDER":1-Male/2-Female
ADNI_demographic_AD <- ADNI_demographic %>%
   filter(DX == 4)

ADNI_demographic_AD %>%
   group_by(GENDER) %>%
   summarise(count=n())
```

Question2:What is the marital status  of the AD patient?
```{r echo = FALSE, warning = FALSE}
#"MARRY":1-Single/2-Married
ADNI_demographic_AD %>%
   group_by(MARRY) %>%
   summarise(count=n())
```

@@@@@@@@@@@@@@@@@@@@@@@  Miss Zhai, pleace check my practice   @@@@@@@@@@@@@@@@@@@@@@@
↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓↓
## 3.Data reshape




## 4.Data visualisation
Work1:To explore the relationship between age and TIV at different stages of disease.
```{r echo = FALSE, warning = FALSE}
ggplot(data = ADNI) +
   geom_point(mapping = aes(x = AGE, y = TIV, color = DX)) 
#geom_point(mapping = aes(x = AGE, y = TIV, color = "red"))
#geom_point(mapping = aes(x = AGE, y = TIV, size = DX))
#geom_point(mapping = aes(x = AGE, y = TIV, alpha = DX))
#geom_point(mapping = aes(x = AGE, y = TIV, shape = DX))
ggplot(data = ADNI) +
   geom_smooth(mapping = aes(x = AGE, y = TIV, color = DX))
```

Work2:To explore the relationship between years of education (EDUCAT) and the volume of the left perihippocampal gyrus (lG_octemp_medParahip_thickness) at marital status (MARRY) and gender.
```{r echo = FALSE, warning = FALSE}
ggplot(data = ADNI) +
   geom_point(mapping = aes(x = EDUCAT, y = lG_octemp_medParahip_thickness , color = "red")) +
   geom_smooth(mapping = aes(x = EDUCAT, y = lG_octemp_medParahip_thickness)) + 
   #facet_wrap(~ DX, nrow = 2)
   facet_wrap(MARRY ~ GENDER)
```

Work3:To count the number of people at different disease stages. 
```{r echo = FALSE, warning = FALSE}
ggplot(data = ADNI) +
   geom_bar(mapping = aes(x = DX, fill = DX))
   #stat_count(mapping = aes(x = DX))
```


Work4:To explore the relationship between years of education (EDUCAT) and different disease stages(DX).
```{r echo = FALSE, warning = FALSE}
ggplot(data = ADNI) +
   stat_summary(
      mapping = aes(x = DX, y = EDUCAT),
      fun.ymin = min,
      fun.ymax = max,
      fun.y = median
      )
```

