---
title: "ADImaging"
author: "Qin"
date: "2019/10/23"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Ⅰ.Introduction 
  ADImagingdata is downloaded on the http://adni.loni.usc.edu/. The data includs 254 samples and 158 variables. All variables includ 5 demographic information(age, gender, education, marital status and APOE4), cortical thickness, mean cortical thickness in 150 brain regions,TIV and total cortical thickness.**The key variable is "ID".**
  
## Ⅱ.Data
```{r echo = FALSE}
#Import the data
library(readxl)
ADNI <- read_excel("ADImaging.xlsx")
```

###Overview
```{r  echo = FALSE}
# View(ADNI)
library(knitr)
kable(ADNI[1:5,2:8],caption="independent variables")
```

### Data Check anf Cleaning
```{r echo = FALSE}
colnames(ADNI)
ADNI[1:6, ]
```

```{r echo = FALSE}
#Only focus on demographic information of AD patients, and order by IDs
#"DX":1-HC/2-EMCI/3-LMCI/AD
library(tidyverse)
library(nycflights13)
ADNI_demographic <-ADNI %>%
   select(ID, DX, AGE, GENDER, EDUCAT, MARRY) %>%
   arrange(ID, DX)
```

Question1:What is the gender of the AD patient?
```{r  echo = FALSE}
#"GENDER":1-Male/2-Female
ADNI_demographic_AD <- ADNI_demographic %>%
   filter(DX == 4)

ADNI_demographic_AD %>%
   group_by(GENDER) %>%
   summarise(count=n())
```

Question2:What is the marital status  of the AD patient?
```{r  echo = FALSE}
#"MARRY":1-Single/2-Married
ADNI_demographic_AD %>%
   group_by(MARRY) %>%
   summarise(count=n())
```

